Technical Report

### 2018-03-20 fully-abstract-comp/technical-report.tex
Update FTLR to trusted/untrusted expression relation.
typos@

The source machine allows for variable length instructions which we utilize for $\scall{o}{}{}$. In other words, when $\scall{o}{}{}$ is decoded, a series of addresses in memory must contain what corresponds to the call instruction (and be within the range of the pc capability). This is described in more detail when we present the decoding function.

@@

% \dominique{22-1-2018: the below is an alternative proposal to the above definition. It is part of a proposed refactoring to simplify the merge the cases for return pointers and closures in the value relation.}
Two expression relations: one for sealed code-data pairs being jumped to and one for capabilities being jumped to in the regular way.
The argument for having one relation relate pairs of pairs of capabilties and the other relate pairs of capabilities is that that is how xjump and regular jumps work: xjump takes pairs while regular jumps take single capabilities.
\begin{align*}
  \lrexj(W) &= \left\{ \npair{\stpair[.]{v_{c,S},v_{d,S}}{v_{c,T},v_{d,T}}} \middle| 
    \begin{array}{l}
      \forall n' \leq n, \src{\reg_S}, \reg_T, \src{\ms_S}, \ms_T, \src{\ms_\stk}, \src{\stk} \ldotp\\
      \quad \forall W_\lrrs , W_\lrm \ldotp \\
      \qquad\npair[n']{[\stpair[.]{v_{c,S}}{v_{c,T}},\stpair[.]{v_{d,T}}{v_{d,S}}]} \in \lrp(W) \wedge \\
      \qquad\npair[n']{\stpair{\reg}{\reg}} \in \lrr (W_\lrrs ) \wedge\\
      \qquad\memSat[n']{\stpair[.]{\ms_S,\stk,\ms_\stk}{\ms_T}}{W_\lrm} \\
      \qquad\Phi_S = \src{(\ms_S,\reg_S,\stk, \ms_\stk)}\\
      \qquad \Phi_S' = \xjumpResult{v_{c,S}}{v_{d,S}}{\Phi_S}\\
      \qquad\Phi_T = (\ms_T,\reg_T)\\
      \qquad\Phi_T' = \xjumpResult{v_{c,T}}{v_{d,T}}{\Phi_T}\\
      \qquad W \oplus W_\lrrs \oplus W_\lrm \\
      \qquad\Rightarrow\npair[n']{\left(\Phi_S', \Phi_T' \right)}\in \lro
    \end{array}
    \right\}\\
  \lre(W) &= \left\{ \npair{\stpair[.]{v_{c,S}}{v_{c,T}}} \middle| 
    \begin{array}{l}
      \forall n' \leq n, \src{\reg_S}, \reg_T, \src{\ms_S}, \ms_T, \src{\ms_\stk}, \src{\stk} \ldotp\\
      \quad \forall W_\lrrs , W_\lrm \ldotp \\
      \qquad\npair[n']{[\stpair[.]{v_{c,S}}{v_{c,T}}]} \in \lrp(W) \wedge \\
      \qquad\npair[n']{\stpair{\reg}{\reg}} \in \lrr (W_\lrrs ) \wedge\\
      \qquad\memSat[n']{\stpair[.]{\ms_S,\stk,\ms_\stk}{\ms_T}}{W_\lrm} \\
      \qquad\Phi_S = \src{(\ms_S,\reg_S,\stk, \ms_\stk)}\\
      \qquad \Phi_S' = \Phi_S \updReg{\pcreg}{v_{c,S}}\\
      \qquad\Phi_T = (\ms_T,\reg_T)\\
      \qquad\Phi_T' = \Phi_T\updReg{\pcreg}{v_{c,T}}\\
      \qquad W \oplus W_\lrrs \oplus W_\lrm\\
      \qquad\Rightarrow\npair[n']{\left(\Phi_S', \Phi_T' \right)}\in \lro
    \end{array}
    \right\}
\end{align*}

@@

\[
  H^\mathrm{code} \; \ta \; \sigma_\baddr \; \sigma_\eaddr \; \code \; s \; \hat{W} = \{\npair{(\code,\code)} | \dom(\code) = [\aaddr,\baddr] \tand \code(a) = \seal{\sigma_\baddr,\sigma_\baddr,\sigma_\eaddr}\}
\]
\lau{19-03-2018: Add the link capabilitiy to the above? code in ta?}
\[
  H^\mathrm{code}_\sigma \; \ta \; s \; \sigma \; \hat{W} = 
  \begin{array}[t]{l}
\left\{
    \begin{array}{l}
\left. \npair{\arraycolsep=0pt\left(\array{l}\sealed{\sigma,\retptrc(\rx,\lin,\baddr,\eaddr,\aaddr'+\calllen - 1)},\\((\rx,\lin),\baddr,\eaddr,\aaddr)\endarray\right)} \middle| \right. \\
      \\
      \begin{array}{l}
        \decInstr{\code([a',a' + \calllen]-1)} = \overline{\scall{o}{r_1}{r_2}} \tand \\
        \aaddr = \aaddr' + \retoffset \tand \\
        \sigma = \sigma_\baddr + o \tand\\
        \lbrack \baddr, \eaddr \rbrack = \dom(\code) \subseteq \ta
      \end{array}

@@

\dominique{19-3-2018: components should contain information about what seals they use and for what (for building return pointers or for building closures). That should facilitate defining reasonable linking (only when seals disjoint), and for defining the condition for full abstraction and the FTLR.}
\begin{definition}
  A program $\program$ with memory segment $\ms_\program$ and $\dom(\ms_\program) = \ta$, is reasonable if for all $n$ and all contexts $\context$ the configuration $\plug{\context}{\program}$ satisfies:
  \begin{itemize}
  \item $\plug{\context}{\program}$ has reasonable calls in $\dom(\ms_\program)$ for $n$ steps.
  \item $\plug{\context}{\program}$ uses linker seals properly for $n$ steps.
  \item $\plug{\context}{\program}$ never passes trusted seals accross the boundary.
  \end{itemize}
\end{definition}

>>>>

The source machine allows for variable length instructions which we utilise for $\scall{o}{}{}$. In other words, when $\scall{o}{}{}$ is decoded, a series of addresses in memory must contain what corresponds to the call instruction (and be within the range of the pc capability). This is described in more detail when we present the decoding function.

@@

% \dominique{22-1-2018: the below is an alternative proposal to the above definition. It is part of a proposed refactoring to simplify the merge the cases for return pointers and closures in the value relation.}
Two expression relations: one for sealed code-data pairs being jumped to and one for capabilities being jumped to in the regular way.
The argument for having one relation relate pairs of pairs of capabilities and the other relate pairs of capabilities is that that is how xjump and regular jumps work: xjump takes pairs while regular jumps take single capabilities.
\begin{align*}
  \lrexjg{\trust}(W) &= \left\{ \npair{\stpair[.]{v_{c,S},v_{d,S}}{v_{c,T},v_{d,T}}} \middle| 
    \begin{array}{l}
      \forall n' \leq n, \src{\reg_S}, \reg_T, \src{\ms_S}, \ms_T, \src{\ms_\stk}, \src{\stk} \ldotp\\
      \quad \forall W_\lrrs , W_\lrm \ldotp \\
      \qquad\npair[n']{[\stpair[.]{v_{c,S}}{v_{c,T}},\stpair[.]{v_{d,T}}{v_{d,S}}]} \in \lrp(W) \wedge \\
      \qquad\npair[n']{\stpair{\reg}{\reg}} \in \lrrg{\trust} (W_\lrrs ) \wedge\\
      \qquad\memSat[n']{\stpair[.]{\ms_S,\stk,\ms_\stk}{\ms_T}}{W_\lrm} \\
      \qquad\Phi_S = \src{(\ms_S,\reg_S,\stk, \ms_\stk)}\\
      \qquad \Phi_S' = \xjumpResult{v_{c,S}}{v_{d,S}}{\Phi_S}\\
      \qquad\Phi_T = (\ms_T,\reg_T)\\
      \qquad\Phi_T' = \xjumpResult{v_{c,T}}{v_{d,T}}{\Phi_T}\\
      \qquad W \oplus W_\lrrs \oplus W_\lrm \\
      \qquad\Rightarrow\npair[n']{\left(\Phi_S', \Phi_T' \right)}\in \lro
    \end{array}
    \right\}\\
  \lreg{\trust}(W) &= \left\{ \npair{\stpair[.]{v_{c,S}}{v_{c,T}}} \middle| 
    \begin{array}{l}
      \forall n' \leq n, \src{\reg_S}, \reg_T, \src{\ms_S}, \ms_T, \src{\ms_\stk}, \src{\stk} \ldotp\\
      \quad \forall W_\lrrs , W_\lrm \ldotp \\
      \qquad\npair[n']{[\stpair[.]{v_{c,S}}{v_{c,T}}]} \in \lrp(W) \wedge \\
      \qquad\npair[n']{\stpair{\reg}{\reg}} \in \lrrg{\trust} (W_\lrrs ) \wedge\\
      \qquad\memSat[n']{\stpair[.]{\ms_S,\stk,\ms_\stk}{\ms_T}}{W_\lrm} \\
      \qquad\Phi_S = \src{(\ms_S,\reg_S,\stk, \ms_\stk)}\\
      \qquad \Phi_S' = \Phi_S \updReg{\pcreg}{v_{c,S}}\\
      \qquad\Phi_T = (\ms_T,\reg_T)\\
      \qquad\Phi_T' = \Phi_T\updReg{\pcreg}{v_{c,T}}\\
      \qquad W \oplus W_\lrrs \oplus W_\lrm\\
      \qquad\Rightarrow\npair[n']{\left(\Phi_S', \Phi_T' \right)}\in \lro
    \end{array}
    \right\}
\end{align*}

@@

\[
  H^\mathrm{code} \; \ta \; \sigma_\baddr \; \sigma_\eaddr \; \code \; s \; \hat{W} = \{\npair{(\code,\code)} | \dom(\code) = [\aaddr,\baddr] \tand \code(a) = \seal{\sigma_\baddr,\sigma_\baddr,\sigma_\eaddr}\}
\]
\lau{19-03-2018: Add the link capability to the above? code in ta?}
\[
  H^\mathrm{code}_\sigma \; \ta \; s \; \sigma \; \hat{W} = 
  \begin{array}[t]{l}
\left\{
    \begin{array}{l}
\left. \npair{\arraycolsep=0pt\left(\array{l}\sealed{\sigma,\retptrc(\rx,\lin,\baddr,\eaddr,\aaddr'+\calllen - 1)},\\((\rx,\lin),\baddr,\eaddr,\aaddr)\endarray\right)} \middle| \right. \\
      \\
      \begin{array}{l}
        \decInstr{\code([a',a' + \calllen]-1)} = \overline{\scall{o}{r_1}{r_2}} \tand \\
        \aaddr = \aaddr' + \retoffset \tand \\
        \sigma = \sigma_\baddr + o \tand\\
        \lbrack \baddr, \eaddr \rbrack = \dom(\code) \subseteq \ta
      \end{array}

@@

\dominique{19-3-2018: components should contain information about what seals they use and for what (for building return pointers or for building closures). That should facilitate defining reasonable linking (only when seals disjoint), and for defining the condition for full abstraction and the FTLR.}
\begin{definition}
  A program $\program$ with memory segment $\ms_\program$ and $\dom(\ms_\program) = \ta$, is reasonable if for all $n$ and all contexts $\context$ the configuration $\plug{\context}{\program}$ satisfies:
  \begin{itemize}
  \item $\plug{\context}{\program}$ has reasonable calls in $\dom(\ms_\program)$ for $n$ steps.
  \item $\plug{\context}{\program}$ uses linker seals properly for $n$ steps.
  \item $\plug{\context}{\program}$ never passes trusted seals across the boundary.
  \end{itemize}
\end{definition}
